Using Monte Carlo to estimate the effects of NHL rule changes

### 2020-12-10 slides.Rmd
fix slides
Added conference gap slide

@@

>>>>

# Conference Gap Definition

- After seeding the teams in each conference, we look at both of the 8th seeds. 
- The 8th seed is the cutoff for which teams make the playoffs 
- The difference between the point totals for the East 8th seed and the point totals for the West 8th seed is the conference gap.

@@

![](Images/GapVis.png)
![](Images/SeedPlace.png)
